%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{Senior Software Engineer} % Job title
	{FST Network} % Organization
	{Taipei, Taiwan} % Location
	{Oct. 2018 - Now} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implement and design Node.js CLI (commander.js) with FST Product LOC.}
			\item {Help business customers analyze problems and provide technical support by using LOC.}
			\item {Implement POC of Event pattern design with Elasticsearch (time series data).}
			\item {Design and implement search mechanism for time series data. Including search by query and pattern matching search with Elasticsearch (EQL, Search API).}
			% \item {Deal with Data Mesh service, FaaS service.}
			\item {Develop backend API of blockchain platform integrated with k8s.}
			\item {Design Authentication \& Authorization mechanism with cloud native solutions (Open Policy Agent, Envoy sidecar pattern).}
			\item {Implement explorer of Ethereum private chain with React}
			\item {Use GraphQL with Relay}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Software Engineer Intern} % Job title
	{Appier} % Organization
	{Taipei, Taiwan} % Location
	{Aug. 2016 - Feb 2018} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Develop in Chinese \& Japanese NLP tools for text preprocessing.}
			\item {Implement an E-commerce Recommendation System with Factorization model.}
			\item {Implement a Network Representation Learning system for recommendation.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Teaching Assistant} % Job title
	{National Chengchi University} % Organization
	{Taipei, Taiwan} % Location
	{Sep. 2016 - Jun. 2018} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Sep. 2016 - Jan. 2017: Computer Programming (I)}
			\item {Feb. 2017 - June. 2017: Social Network Application}
			\item {Sep. 2017 - Jan. 2018: Introduction to Digital Contents and Technologies}
			\item {Feb. 2018 - Jun. 2018: Web Search and Mining}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}
